Are We Teaching Cybersecurity (and how well)?\\(Abstract 20 January, Paper 27th)

### 2019-01-05 ITiCSE2019.tex
JHD added quote from Michael Page, but pointed to ESG

\subsection{Staff}
It is well known that CyberSecurity skills are in short supply, for example \cite{Page2018a}.
\begin{quote}

>>>>

\subsection{Staff}
It is well known that CyberSecurity skills are in short supply, for example \cite{Page2018a}.
\begin{quote}
% JHD: I am in touch with ESG to try to find more, and someUK-specific numbers.
Research into the state of IT conducted annually by ESG\footnote{Apparently \url{https://www.esg-global.com/research/esg-brief-2018-cybersecurity-spending-trends}.} has revealed that the skills gap in information security continues to widen and has doubled in the past five years. In 2014, 23\% of respondents to the survey stated that their organisation had a problematic shortage of information security skills. This had climbed to 51\% at the beginning of this year. Clearly, this is an issue which is being felt across many industries and organisations, and is a concern which extends beyond IT leadership into the boardroom.
\end{quote}
\begin{quote}
